Commutative character sheaves and geometric types for supercuspidal representations

### 2017-06-28 Geometric types.tex
Promoted Lemma to Proposition in Rigidification.

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CS\der(G)$.
\end{proposition}
\begin{proof}
%In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
Moreover, using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CS\der(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab)).
\end{array}
\]
and on morphisms by $\alpha \mapsto L(\alpha)$.
The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
\end{proof}

@@

\begin{lemma}\label{lemma:nubeta}
Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
\end{lemma}

\begin{proof}
We begin by defining a functor $\CS\ab(G) \to \CS\der(G)$.
Let $j\der : G\der \to G$ be the kernel of $q:G \to G\ab$ 
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (j\der(h),g)$.
Then for $(\cs{L},\mu,\nu) \in \CS\der(G)$, define $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ by the following diagram.
\begin{equation}\label{eqn:betanu}
\begin{tikzcd}
& n^* \cs{L} \arrow[equal]{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
\end{tikzcd}
\end{equation}
Then $\beta = r\der \circ j^*(\nu)$, where $r\der : (\cs{L}_1)_{G\der} \to (\EE)_{G\der}$ is the isomorphism of constant local systems  determined by the rigidification $r: \cs{L}_1 \to \EE$ of $\cs{L}$ determined by $\mu$ (see \cite{cunningham-roe:13a}*{Remark~1.11}) so that
\begin{equation}\label{eqn:rigidification}
\begin{tikzcd}
\cs{L}_1 \arrow{r}{r} \arrow{d}{\mu_{(1,1)}}  & \EE \arrow[equal]{d} \\
\cs{L}_1\otimes\cs{L}_1 \arrow{r}{r\otimes r}  & \EE\otimes  \EE
\end{tikzcd}
\end{equation}
commutes where, as usual, $=$ denotes a canonical isomorphism.
%
To show that $(\cs{L},\mu,\beta) \in \CS\ab(G)$, we must see that $\beta$ is a morphism in $\CS(G\der)$ by showing that the following diagram commutes in $\Loc(G\der^2)$.
\begin{equation}\label{eqn:betaGder}
\begin{tikzcd}
m\der^*\cs{L}\vert_{G\der} \arrow{rr}{m\der^* \beta} \arrow[equal]{d} && \arrow[equal]{d} (\EE)_{G\der^2}\\
\cs{L}\vert_{G\der} \boxtimes \cs{L}\vert_{G\der} \arrow{rr}{\beta\boxtimes\beta} &&  (\EE)_{G\der}\boxtimes (\EE)_{G\der} 
\end{tikzcd}
\end{equation}
By Proposition~\ref{prop:CSGabab}, $\cs{L} = q^*\cs{L}\ab$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
Thus, $\cs{L}\vert_{G\der} = (\cs{L}_1)_{G\der}$ and the diagram above becomes a diagram of constant Weil local systems on $G\der^2$.
We can therefore test  whether  diagram commutes by evaluating all local systems at $(1,1)\in G\der^2$.  Doing this recovers \eqref{eqn:rigidification} from \eqref{eqn:betaGder}, so \eqref{eqn:rigidification} commutes.
%
After confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$, this concludes the definition of the functor  $\CS\ab(G) \to \CS\der(G)$.

>>>>

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CS\der(G)$.
\end{proposition}
\begin{proof}
Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
Moreover, using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
\[
\begin{array}{rcl}
\CS(G\ab) &\to& \CS\der(G) \\
(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab)).
\end{array}
\]
and on morphisms by $\alpha \mapsto L(\alpha)$.
The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
\end{proof}

@@

\begin{proposition}\label{prop:nubeta}
The categories $\CS\ab(G)$ and $\CS(G\ab)$ are equivalent.
\end{proposition}

\begin{proof}
In light of Proposition~\ref{prop:CSGabab}, it suffices to exhibit an equivalence  between $\CS\der(G)$ and $\CS\ab(G)$.

We begin by defining a functor $\CS\ab(G) \to \CS\der(G)$.
Let $j\der : G\der \to G$ be the kernel of $q:G \to G\ab$ 
Define $k: G\der\times G\to G\times G$ by $k(h,g) = (j\der(h),g)$.
Then for $(\cs{L},\mu,\nu) \in \CS\der(G)$, define $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ by the following diagram.
\begin{equation}\label{eqn:betanu}
\begin{tikzcd}
& n^* \cs{L} \arrow[equal]{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
\end{tikzcd}
\end{equation}
Then $\beta = r\der \circ j^*(\nu)$, where $r\der : (\cs{L}_1)_{G\der} \to (\EE)_{G\der}$ is the isomorphism of constant local systems  determined by the rigidification $r: \cs{L}_1 \to \EE$ of $\cs{L}$ determined by $\mu$ (see \cite{cunningham-roe:13a}*{Remark~1.11}) so that
\begin{equation}\label{eqn:rigidification}
\begin{tikzcd}
\cs{L}_1 \arrow{r}{r} \arrow{d}{\mu_{(1,1)}}  & \EE \arrow[equal]{d} \\
\cs{L}_1\otimes\cs{L}_1 \arrow{r}{r\otimes r}  & \EE\otimes  \EE
\end{tikzcd}
\end{equation}
commutes where, as usual, $=$ denotes a canonical isomorphism.
%
To show that $(\cs{L},\mu,\beta) \in \CS\ab(G)$, we must see that $\beta$ is a morphism in $\CS(G\der)$ by showing that the following diagram commutes in $\Loc(G\der^2)$.
\begin{equation}\label{eqn:betaGder}
\begin{tikzcd}
m\der^*\cs{L}\vert_{G\der} \arrow{rr}{m\der^* \beta} \arrow[equal]{d} && \arrow[equal]{d} (\EE)_{G\der^2}\\
\cs{L}\vert_{G\der} \boxtimes \cs{L}\vert_{G\der} \arrow{rr}{\beta\boxtimes\beta} &&  (\EE)_{G\der}\boxtimes (\EE)_{G\der} 
\end{tikzcd}
\end{equation}
By Proposition~\ref{prop:CSGabab}, $\cs{L} = q^*\cs{L}\ab$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
Thus, $\cs{L}\vert_{G\der} = (\cs{L}_1)_{G\der}$ and the diagram above becomes a diagram of constant Weil local systems on $G\der^2$.
We can therefore test  whether  diagram commutes by evaluating all local systems at $(1,1)\in G\der^2$.  Doing this recovers \eqref{eqn:rigidification} from \eqref{eqn:betaGder}, so \eqref{eqn:rigidification} commutes.
%
After confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$, this concludes the definition of the functor  $\CS\ab(G) \to \CS\der(G)$.
